Scheeper's Meager-NWD Game and the Menger Game

### 2014-05-14 phd/dissertation/chapter2.tex

Games may be modeled mathematically in various ways,
but we will find it convenient to think of them in terms defined by
Gale and Stewart. \cite{gale}

@@

As an illustration of an infinite game, we may consider a simple example due to
Baker \cite{baker}.

@@

Topological games are usually infinite games, ignoring trivial examples.
One of the earliest examples
of a topological game is the Banach-Mazur game, proposed by Stanislaw Mazur
as Problem 43 in Stefan Banach's Scottish Book (1935). A more comprehensive
history of the Banacy-Mazur and other topological games may be found in
Telgarsky's survey on the subject \cite{telgarsky}.

@@

The Borel Determinacy Theorem states that $G=\<M,W\>$ is determined whenever
$W$ is a Borel subset of $M^\omega$ \cite{martin}. It's an easy corollary that
all finite games are determined; $W$ must be clopen.

@@

\begin{proof}
  Adapted from \cite{baker}.
  Let $X=\{x_0,x_1,\dots\}$. Let $i(a,b)$ be the least integer such that
  $a<x_{i(x,y)}<b$, if it exists. We define a strategy $\sigma$ for $\pl B$
  such that:
  \begin{itemize}
    \item $\sigma(\<a_0\>)=x_{i(a_0,\infty)}$.
          If $i(a_0,\infty)$ does not exist, then the choice of $\sigma(\<a_0\>)$
          is arbitary, say, $a_0+1$.
    \item $\sigma(\<a_0,...,a_{n+1}\>)=x_{i(a_{n+1},b_n)}$, where
          $b_n=\sigma(\<a_0,\dots,a_n\>)$.
          If $i(a_{n+1},b_n)$ does not exist, then the choice of
          $\sigma(\<a_0,...,a_{n+1}\>)$ is arbitrary, say,
          $
            \sigma(\<a_0,...,a_{n+1}\>)
              =
            \frac{a_{n+1}+b_n}{2}
          $.
  \end{itemize}

@@

This yields a classical result.

@@

\begin{thm}
$\pl E\not\win \bmgame{X}$ if and only if $X$ is a Baire space. \cite{haworth}
\end{thm}

@@

Those arrows may not be reversed. A Bernstein subset of the real line is an
example of a Baire space which is not weakly $\alpha$-favorable, and

>>>>

Games may be modeled mathematically in various ways,
but we will find it convenient to think of them in terms defined by
Gale and Stewart. \cite{MR0054922}

@@

As an illustration of an infinite game, we may consider a simple example due to
Baker \cite{noMRbaker}.

@@

Topological games are usually infinite games, ignoring trivial examples.
One of the earliest examples
of a topological game is the Banach-Mazur game, proposed by Stanislaw Mazur
as Problem 43 in Stefan Banach's Scottish Book (1935). A more comprehensive
history of the Banacy-Mazur and other topological games may be found in
Telgarsky's survey on the subject \cite{MR892457}.

@@

The Borel Determinacy Theorem states that $G=\<M,W\>$ is determined whenever
$W$ is a Borel subset of $M^\omega$ \cite{MR0403976}. It's an easy corollary that
all finite games are determined; $W$ must be clopen.

@@

\begin{proof}
  Adapted from \cite{noMRbaker}.
  Let $X=\{x_0,x_1,\dots\}$. Let $i(a,b)$ be the least integer such that
  $a<x_{i(x,y)}<b$, if it exists. We define a strategy $\sigma$ for $\pl B$
  such that:
  \begin{itemize}
    \item $\sigma(\<a_0\>)=x_{i(a_0,\infty)}$.
          If $i(a_0,\infty)$ does not exist, then the choice of $\sigma(\<a_0\>)$
          is arbitary, say, $a_0+1$.
    \item $\sigma(\<a_0,...,a_{n+1}\>)=x_{i(a_{n+1},b_n)}$, where
          $b_n=\sigma(\<a_0,\dots,a_n\>)$.
          If $i(a_{n+1},b_n)$ does not exist, then the choice of
          $\sigma(\<a_0,...,a_{n+1}\>)$ is arbitrary, say,
          $
            \sigma(\<a_0,...,a_{n+1}\>)
              =
            \frac{a_{n+1}+b_n}{2}
          $.
  \end{itemize}

@@

More informally, $\pl B$ can force a win by enumerating the countable set
$X$ and playing every legal choice by the end of the game.
This yields a classical result.

@@

\begin{thm}
$\pl E\not\win \bmgame{X}$ if and only if $X$ is a Baire space.
\cite{MR0431104}
\end{thm}

@@

Those arrows may not be reversed. A Bernstein subset of the real line is an
example of a Baire space which is not weakly $\alpha$-favorable, and Gabriel
Debs constructed an example of a completely regular space for which $\pl N$
has a winning $2$-tactic, but lacks a winning $1$-tactic. \cite{MR817083}
